\BigGap
\SubSection
{Conferences}
{Conferences}
{PDF:Conferences}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}


\Gap
\NumberedItem{[13]}
{
\underline{Link, G. J.P.}, \& Germonprez, M. (2018). Assessing open source project health. In Twenty-fourth Americas Conference on Information Systems 2018 Proceedings. New Orleans, LA.
}

\Gap
\NumberedItem{[12]}
{
Rao, M., \underline{Link, G. J.P.}, Marti, D., Leak, A., \& Bodo, R. (2018). A trading market for prices in peer production. In ACM Collective Intelligence 2018 Proceedings. Zurich, Switzerland.
}

\Gap
\NumberedItem{[11]}
{
Rao, M., \underline{Link, G. J.P.}, Marti, D., Leak, A., \& Bodo, R. (2018). A Trading Market to Incentivize Secure Software. In 17th Annual Workshop on the Economics of Information Security (WEIS), Innsbruck, Austria.
}

\Gap
\NumberedItem{[10]}
\href{https://doi.org/10.1145/3148330.3148333}
{
Gandhi, R., Germonprez, M., \& \underline{Link, G. J.P.}\footnotemark (2018). Open data standards for open source software risk management routines: An examination of SPDX. Presented at the ACM GROUP’18, Sanibel Island. \url{https://doi.org/10.1145/3148330.3148333}
}
\footnotetext{Authors in alphabetical order}

\Gap
\NumberedItem{[9]}
\href{http://hdl.handle.net/10125/50190}
{
\underline{Link, G. J.P.}, \& Qureshi, S. (2018). The role of open source communities in development: Policy implications for governments. Presented at the HICSS 2018, Hawaii.
\url{http://hdl.handle.net/10125/50190}
}

\Gap
\NumberedItem{[8]}
\href{https://doi.org/10.1145/3126673.3126679}
{
\underline{Link, G. J.P.} (2017). The value of engaging with open source communities. In \textit{OpenSym ’17 Companion}. Galway, Ireland: ACM. \url{https://doi.org/10.1145/3126673.3126679}
}

\Gap
\NumberedItem{[7]}
\href{https://doi.org/10.1145/3125433.3125472}
{
\underline{Link, G. J.P.}, \& Jeske, D. (2017). Understanding organization and open source community relations through the Attraction-Selection-Attrition Model. In \textit{OpenSym ’17 Companion}. Galway, Ireland: ACM. \url{https://doi.org/10.1145/3125433.3125472}
}

\Gap
\NumberedItem{[6]}
\href{http://aisel.aisnet.org/amcis2017/ICTs/Presentations/18/}
{
\underline{Link, G. J.P.}, \& Qureshi, S. (2017). The role of open source in new business formation: Innovations for development. In \textit{Proceedings of the Twenty-third Americas Conference on Information Systems}. Boston. Retrieved from \url{http://aisel.aisnet.org/amcis2017/ICTs/Presentations/18/}
}

\Gap
\NumberedItem{[5]}
\href{http://aisel.aisnet.org/mwais2017/43/}
{
\underline{Link, G. J.P.}, Gill, J., \& Khazanchi, D. (2017). Measuring adoption of open source software and practices in organizations: A pilot study. In \textit{Proceedings of the Twelfth Midwest Association for Information Systems Conference}. Springfield, IL. Retrieved from \url{http://aisel.aisnet.org/mwais2017/43/}
}

\Gap
\NumberedItem{[4]}
\href{http://aisel.aisnet.org/mwais2017/44}
{
\underline{Link, G. J.P.}, Lumbard, K., Germonprez, M., \& Goggins, S. (2017). Advancing open online community science practice: The open community data exchange. In \textit{Proceedings of the Twelfth Midwest Association for Information Systems Conference}. Springfield, IL. \url{http://aisel.aisnet.org/mwais2017/44}
}

\Gap
\NumberedItem{[3]}
\href{https://doi.org/10.1145/2962132.2962142}
{
\underline{Link, G. J.P.}, Germonprez, M., Goggins, S., Hemsley, J., Rand, B., \& Squire, M. (2016). The Open Community Data Exchange: Advancing data sharing and discovery in open online community science. In \textit{OpenSym ’16 Companion}. Berlin, Germany: ACM. \url{https://doi.org/10.1145/2962132.2962142}
}

\Gap
\NumberedItem{[2]}
\href{http://aisel.aisnet.org/amcis2016/Open/Presentations/7/}
{
\underline{Link, G. J.P.}, \& Germonprez, M. (2016). Understanding open source communities as complex adaptive systems: A case of the R Project community. In AMCIS 2016 Proceedings. San Diego, CA. Retrieved from \url{http://aisel.aisnet.org/amcis2016/Open/Presentations/7/}
}

\Gap
\NumberedItem{[1]}
\href{https://doi.org/10.1007/978-3-319-22747-4_3}
{
\underline{Link, G. J.P.}, Siemon, D., de Vreede, G.-J., \& Robra-Bissantz, S. (2015). 
Evaluating Anchored Discussion to Foster Creativity in Online Collaboration. 
In N. Baloian, Y. Zorian, P. Taslakian, \& S. Shoukouryan (Eds.), Collaboration and Technology (pp. 28--44). 
Springer International Publishing. 
\url{https://doi.org/10.1007/978-3-319-22747-4_3}
}


\endgroup