\BigGap
\SubSection
{Presentations}
{Presentations}
{PDF:Presentations}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\Gap
\NumberedItem{[13]}
{
Link, G. J.P. (2018, March). Engaging Volunteers and Voluntolds in Open Source Projects. Presented at the 10th Annual Research and Creative Activity Fair, University of Nebraska at Omaha, NE, USA. \url{https://digitalcommons.unomaha.edu/srcaf/2018/schedule/148/}
}

\Gap
\NumberedItem{[12]}
{
Germonprez, M., \& Link, G. J. P. (2017, September). BoF: Community Health Analytics for Open Source. Birds-of-a-Feather presented at the Open Source Summit North America, Los Angeles, California. Retrieved from \url{http://sched.co/BCsP}
}

\Gap
\NumberedItem{[11]}
{
Link, G. J.P. (2017, August). Understanding organization and open source community relations through the Attraction-Selection-Attrition Model. Presented at OpenSym 2017, Galway, Ireland.
}

\Gap
\NumberedItem{[10]}
{
Link, G. J.P. (2017, August). The value of engaging with open source communities. Presented at the OpenSym 2017 Doctoral Consortium, Galway, Ireland.
}

\Gap
\NumberedItem{[9]}
{
Link, G. J.P. (2017, August). The role of open source in new business formation: Innovations for development. Presented at the Twenty-third Americas Conference on Information Systems, Boston, MA.
}

\Gap
\NumberedItem{[8]}
{
Link, G. J.P., \& Lumbard, K. (2017, May). Advancing open online community science practice: The open community data exchange. Presented at the Twelfth Midwest Association for Information Systems Conference. Springfield, IL.
}

\Gap
\NumberedItem{[7]}
{
Link, G. J.P. (2017, May). Measuring adoption of open source software and practices in organizations: A pilot study. Presented at the Twelfth Midwest Association for Information Systems Conference. Springfield, IL.
}

\Gap
\NumberedItem{[6]}
{
Link, G. J.P. (2016, December). Moving Open Source Communities:  How Foundations Onboard Communities. Presented at the SIGOPEN Developmental Workshop at ICIS 2016, Dublin, Ireland.
}

\Gap
\NumberedItem{[5]}
{
Link, G. J.P., \& Lumbard, K. (2016, December). Communication Technology Selection in a Young Open Source Community:  A Case of the Hyperledger Project. Presented at the SIGOPEN Developmental Workshop at ICIS 2016, Dublin, Ireland.
}

\Gap
\NumberedItem{[4]}
{
Link, G. J.P. (2016, August). The Open Community Data Exchange: Advancing Data Sharing and Discovery in Open Online Community Science. Presented at the OpenSym 2016, Berlin, Germany.
}

\Gap
\NumberedItem{[3]}
{
Link, G. J.P. (2016, April). The Guided Evolution of Open Source Communities. Presented at the 14th Annual BigXII+MISResearchSymposium, Baylor University, Waco, TX, USA.
}

\Gap
\NumberedItem{[2]}
{
Link, G. J.P. (2016, March). The Guided Evolution of Open Source Communities. Presented at the 8th Annual Research and Creative Activity Fair, University of Nebraska at Omaha, NE, USA. \url{http://digitalcommons.unomaha.edu/srcaf/2016/Schedule/56/}
}

\Gap
\NumberedItem{[1]}
{
Link, G. J.P. (2015, November). The Movement and Commoditization of Open Source Communities. Presented at the INFORMS Annual Meeting 2015, Philadelphia, PA, USA.
}

\endgroup


